NLA17 Dissolved Gas Spatial Autocorrelation

### 2019-10-29 scripts/laggedScatterplot.Rmd
Added self_contained to YAML, but still producing *_files folder.

---
title: "NLA17 Dissolved Gas Spatial Autocorrelation"
author: "J. Beaulieu"
date: "10/28/2019"
output: html_document
---

@@

hscat(dissolved.co2 ~ 1,  
      dg.sp[!is.na(dg.sp$dissolved.co2), ], # remove missing
      # 5617275m = 3490 miles. AK to FL
      c(0, 1000, 2000, 3000, 4000, 5000, 6000))

hscat(dissolved.n2o ~ 1,  
      dg.sp[!is.na(dg.sp$dissolved.n2o), ], # remove missing
      # 5617275m = 3490 miles. AK to FL
      c(0, 1000, 2000, 3000, 4000, 5000, 6000))

>>>>

---
title: "NLA17 Dissolved Gas Spatial Autocorrelation"
author: "J. Beaulieu"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    self_contained: yes
    mode: selfcontained
---

@@

# hscat(dissolved.co2 ~ 1,  
#       dg.sp[!is.na(dg.sp$dissolved.co2), ], # remove missing
#       # 5617275m = 3490 miles. AK to FL
#       c(0, 1000, 2000, 3000, 4000, 5000, 6000)) 
# 
# hscat(dissolved.n2o ~ 1,  
#       dg.sp[!is.na(dg.sp$dissolved.n2o), ], # remove missing
#       # 5617275m = 3490 miles. AK to FL
#       c(0, 1000, 2000, 3000, 4000, 5000, 6000))
